---
title: "Python_DeepLearning_3.4"
author: "PoMingChen"
date: "3/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
use_python("/Users/chenpoming/anaconda3/envs/m-team2/bin/python", required = T)
use_condaenv("m-team2")
```


```{python}
# from keras import models
# from keras import layers
# model = models.Sequential()
# model.add(layers.Dense(32, input_shape=(784,)))
# model.add(layers.Dense(32))
# 
# print(model)
```

### Layers

2. layer -> layers to be a model -> Loss function and Optimizer(under SGD)

```{python}
from keras import layers
layer = layers.Dense(32, input_shape=(784,))

print(layer)
```

### Keras

1. Keras and TensorFlow 差在哪邊？

2. Developing overview

- Define your training data

- Define a network of layers (or model)

- Configure the learning process by choosing a loss function, an optimizer, and some metrics to monitor.

- Iterate on your training data by calling the `fit()` method of your model

```{python}
from keras import models
from keras import layers
model = models.Sequential()
model.add(layers.Dense(32, activation='relu', input_shape=(784,)))
model.add(layers.Dense(10, activation='softmax'))
```

same model as above defined using functionl API

**何謂functional API? (ON CHAPTER 7**
```{python}
# input_tensor = layers.Input(shape=(784,))
# x = layers.Dense(32, activation='relu')(input_tensor)
# output_tensor = layers.Dense(10, activation='softmax')(x)
# model = models.Model(inputs=input_tensor, outputs=output_tensor)
# 
# from keras import optimizers
# model.compile(optimizer=optimizers.RMSprop(lr=0.001),loss='mse',metrics=['accuracy'])
# # model.fit(input_tensor, target_tensor, batch_size=128, epochs=10)
# #input_tensor就是input data
# #target_tensor就是output data的概念
```

### set up deep-learning workstation

> If you’re seriousabout deep learning, you should set up a local workstation with one or more GPUs

### 3.4 Classifying movie reviews: a binary classification example

這不是子婷當初寒假跟我聊到的case！？

```{python}
from keras.datasets import imdb
(train_data, train_labels), (test_data, test_labels) = imdb.load_data(num_words=10000)
#The argument num_words=10000 means you’ll only keep the top 10,000 most fre-quently occurring words in the training data. Rare words will be discarded. This allowsyou to work with vector data of manageable size.
```

```{python}
train_data[0]
train_labels[0]
#where 0 stands for negative and 1 stands for positive:
```

```{python}
word_index = imdb.get_word_index()
reverse_word_index = dict([(value, key) for (key, value) in word_index.items()])
decoded_review = ' '.join([reverse_word_index.get(i - 3, '?') for i in train_data[0]])
```

#### Listing 3.2
```{python}
import numpy as np
def vectorize_sequences(sequences, dimension=10000):
  results = np.zeros((len(sequences), dimension))
  for i, sequence in enumerate(sequences):
    results[i, sequence] = 1.
  return results
x_train = vectorize_sequences(train_data)
x_test = vectorize_sequences(test_data)
```

```{python}
x_train[0]
```

```{python}
y_train = np.asarray(train_labels).astype('float32')
y_test = np.asarray(test_labels).astype('float32')

y_test
y_train
```

#### Listing 3.3 The Model Definition(the whole model)
```{python}
from keras import models
from keras import layers

model = models.Sequential() #另一個方式是functional api
model.add(layers.Dense(16, activation='relu', input_shape=(10000,))) #第一層
model.add(layers.Dense(16, activation='relu')) #第二層
model.add(layers.Dense(1, activation='sigmoid')) #第三層（結果輸出）（1or0）（a probalility to be 1 or 0)
```

#### Listing 3.4 Compelling the model
```{python}
model.compile(optimizer='rmsprop',
              loss='binary_crossentropy',
              metrics=['accuracy'])
```

#### Listing 3.5 Configuring the optimizer
```{python}
from keras import optimizers
model.compile(optimizer=optimizers.RMSprop(lr=0.001),
              loss='binary_crossentropy',
              metrics=['accuracy'])
```

#### Listing 3.6 Using the custom losses and metrics
```{python}
from keras import losses
from keras import metrics
model.compile(optimizer=optimizers.RMSprop(lr=0.001),
              loss=losses.binary_crossentropy,
              metrics=[metrics.binary_accuracy])
```

#### Listing 3.7 Setting aside a validation set
```{python}
x_val = x_train[:10000]
partial_x_train = x_train[10000:]
y_val = y_train[:10000]
partial_y_train = y_train[10000:]
```

#### Listing 3.8 Training the model
```{python}
model.compile(optimizer='rmsprop',
              loss='binary_crossentropy',
              metrics=['acc'])
              
history = model.fit(partial_x_train,
                    partial_y_train,
                    epochs=20,
                    batch_size=512,
                    validation_data=(x_val, y_val))
```

```{python}
# import matplotlib.pyplot as plt
# history_dict = history.history
# loss_values = history_dict['loss']
# val_loss_values = history_dict['val_loss']
# epochs = range(1, len(acc) + 1)
# plt.plot(epochs, loss_values, 'bo', label='Training loss')
# plt.plot(epochs, val_loss_values, 'b', label='Validation loss')
# plt.title('Training and validation loss')
# plt.xlabel('Epochs')
# plt.ylabel('Loss')
# plt.legend()
# plt.show()
```



It seems to be some problem on Listing 3.9 3.10 (the plots), so let's move on Listing 3.11


#### Listing 3.11 Retraining the model from scratch
```{python}
model = models.Sequential()
model.add(layers.Dense(16, activation='relu', input_shape=(10000,)))
model.add(layers.Dense(16, activation='relu'))
model.add(layers.Dense(1, activation='sigmoid'))
model.compile(optimizer='rmsprop',
              loss='binary_crossentropy',
              metrics=['acc'])
              
model.fit(x_train, y_train, epochs=4, batch_size=512)
results = model.evaluate(x_test, y_test)
```

```{python}
model.predict(x_test)
```

