---
title: "Deep Learning"
author: "陳宜榛"
date: "3/19/2019"
output: html_document
---
# Environment setup{-}

```{r}
library(reticulate)
use_python("/Users/jane/anaconda3/envs/m-team-machine-learning/bin/python",
           required = T)
use_condaenv("m-team-machine-learning")
```


```{r, eval=FALSE}
conda_install(envname="m-team-machine-learning",
              c("keras","tensorflow","pip","matplotlib"),
              pip=TRUE)
```

# CH3 {-}

```{python}
from keras import models
from keras import layers
model = models.Sequential()
model.add(layers.Dense(32, activation='relu', input_shape=(784,)))
model.add(layers.Dense(10, activation='softmax'))
```

```{python}
input_tensor = layers.Input(shape=(784,))
x = layers.Dense(32, activation='relu')(input_tensor)
output_tensor = layers.Dense(10, activation='softmax')(x)
model = models.Model(inputs=input_tensor, outputs=output_tensor)
```

```{python}
from keras import optimizers
model.compile(optimizer=optimizers.RMSprop(lr=0.001),
loss='mse',
metrics=['accuracy'])
```

# 3.4 Classifying movie reviews:a binary classification example

## 引入資料（The IMDB dataset）

### Loading the IMDB dataset

```{python}
from keras.datasets import imdb
(train_data, train_labels), (test_data, test_labels) = imdb.load_data(
num_words=10000) #在訓練集中留下前10,000個最常出現的詞
```

> how you can quickly decode one of these reviews back to English words:

```{python}
word_index = imdb.get_word_index()
reverse_word_index = dict(
[(value, key) for (key, value) in word_index.items()])
decoded_review = ' '.join(
[reverse_word_index.get(i - 3, '?') for i in train_data[0]])
```

## 處理資料（Preparing the data）

### Encoding the integer sequences into a binary matrix

```{python}
import numpy as np
def vectorize_sequences(sequences, dimension=10000):
  results = np.zeros((len(sequences), dimension))
  for i, sequence in enumerate(sequences):
    results[i, sequence] = 1.
  return results
x_train = vectorize_sequences(train_data)
x_test = vectorize_sequences(test_data)
y_train = np.asarray(train_labels).astype('float32')
y_test = np.asarray(test_labels).astype('float32')
```

## 建神經網絡（Building your network）

### The model definition

```{python}
from keras import models
from keras import layers
model = models.Sequential()
model.add(layers.Dense(16, activation='relu', input_shape=(10000,)))
model.add(layers.Dense(16, activation='relu')) # Two intermediate layers with 16 hidden units each
model.add(layers.Dense(1, activation='sigmoid')) # A third layer that will output the scalar prediction regarding the sentiment of the current review
```

### Compiling the model

```{python}
model.compile(optimizer='rmsprop',
loss='binary_crossentropy',
metrics=['accuracy'])
```

### Configuring the optimizer

```{python}
from keras import optimizers
model.compile(optimizer=optimizers.RMSprop(lr=0.001),
loss='binary_crossentropy',
metrics=['accuracy'])
```

### Using custom losses and metrics

```{python}
from keras import losses
from keras import metrics
model.compile(optimizer=optimizers.RMSprop(lr=0.001),
loss=losses.binary_crossentropy,
metrics=[metrics.binary_accuracy])
```

## 驗證（Validating your approach）

### Setting aside a validation set

```{python}
x_val = x_train[:10000]
partial_x_train = x_train[10000:]
y_val = y_train[:10000]
partial_y_train = y_train[10000:]
```

### Training your model

```{python}
model.compile(optimizer='rmsprop',
loss='binary_crossentropy',
metrics=['acc'])
history = model.fit(partial_x_train,
partial_y_train,
epochs=20,
batch_size=512,
validation_data=(x_val, y_val))
```

```{python}
history_dict = history.history
history_dict.keys()
```

### Plotting the training and validation loss

```{python}
import matplotlib.pyplot as plt
history_dict = history.history
loss_values = history_dict['loss']
val_loss_values = history_dict['val_loss']
epochs = range(1, len(acc) + 1)
plt.plot(epochs, loss_values, 'bo', label='Training loss')
plt.plot(epochs, val_loss_values, 'b', label='Validation loss')
plt.title('Training and validation loss')
plt.xlabel('Epochs')
plt.ylabel('Loss')
plt.legend()
plt.show()
```

